Review: The Prevalence of Adaptive Introgression in Crop Histories

### 2018-06-27 paper.tex
edits to adaptation questions

\subsection*{Over what timescales and in what genomic regions can we reliably detect adaptive introgression?}
Introgressed haplotypes are most easily detected with limited recombination post-hybridization.
Therefore, recent introgressions (limited meioses) or those occurring in low recombination regions such as centromeres or inversions are preferentially detected.
Moreover, since recombination will progressively degrade tracts of introgression, the genome-wide distribution of tract lengths based on a genetic map can be used to date introgression events (as in \cite{Poets2015}).
Mutation rate, effective population size, and strength of selection on introgressed alleles may also influence the rate of breakup of introgressed chromosomal regions.
Detection of introgression will also be affected by the extent of divergence of donor taxa from a crop's wild progenitor; highly divergent introgressed haplotypes will be easier to identify.

>>>>

\subsection*{Over what timescales and in what genomic regions can we reliably detect adaptive introgression?}
Introgressed haplotypes are most easily detected with limited recombination post-hybridization.
Therefore, recent introgressions (limited meioses) or those occurring in low recombination regions such as centromeres or inversions are preferentially detected.
While this can be problematic for the detection of ancient introgression, the fact that recombination degrades tracts of introgression at a relatively constant and predictable rate allows use of the genome-wide distribution of introgression tract lengths to date initial hybridization (as in \cite{Poets2015}).
Detection of introgression will also be affected by mutation rate, effective population size, the strength of selection on introgressed alleles, and the extent of divergence between donor taxa and a crop's wild progenitor (\emph{e.g.}, highly divergent introgressed haplotypes will be easier to identify).
